The increase in network traffic and the need to increase the capacity
and performance of the stretches of transport networks, born the interest
in elastic networks. At present, the optical transport technology
used in optical networks is Wavelength Division Multiplexing (WDM);
this technology has the capacity to transport, route and assign (Routing
Wavelength Assigment) multiple channels in a same fiber based on carriers
of different wavelengths. This implies that channels with little demand
than the maximum supported, underutilize resources. Therefore, the
flexibility of the spectral grid would be the solution, allowing transmission,
routing and allocation. (RSA - Rounting and Spectrum Allocation) of
channels with variable bandwidth that adjust to the demand. In WDM
networks, routing planning and wavelength allocation algorithms (RWA)
search for a physical route through the network and assign a wavelength
for transport, the selection of that wavelength is conditioned to
be the same during the route of the physical route, this condition
is called a condition of continuity. In the elastic optical networks,
the algorithms of routing planning and spectrum allocation (RSA),
apart from the aforementioned condition, there is a new condition,
which is the condition of contiguity in the spectrum. This condition
stipulates that the frequencies slots that occupy each channel must
be together in the spectrum. The RSA problem can be attacked as routing
and spectrum allocation together. With this approach to the RSA problem,
the greatest difficulty that arises is the large number of conditions
posed by the problem; a greater computational complexity is introduced
when calculating the optimal path for each request while optimizing
the spectrum allocation. The heuristic proposed in this paper is a
multiobjective evolutionary algorithm that determines a set of optimal
Pareto solutions that are not dominated with respect to the others
for the RSA problem. The different tests performed with this algorithm
show promising results with respect to the paper presented in {[}16{]}. 
